Roster Review (Generic)

### 2019-09-02 rosterReview_generic.Rmd
Latest rosters to start the playoffs

free_agent_compare %>% 
  # select(team, name_full, positions, type, zar) %>% 
  select(team, name_full, positions, type, zar, g:war, z_r:z_whip)
  View("Available Free Agents Expanded")

>>>>

free_agent_compare %>% 
  # select(team, name_full, positions, type, zar) %>% 
  select(team, name_full, positions, type, zar, g:war, z_r:z_whip) %>% 
  View("Available Free Agents Expanded")
